% Created 2015-08-01 Sat 22:42
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\providecommand{\alert}[1]{\textbf{#1}}

\title{\textbf{TODO} LIST}
\author{Grand}
\date{2015-07}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.9.3f}}

\begin{document}

\maketitle

\setcounter{tocdepth}{3}
\tableofcontents
\vspace*{1cm}


\section{Code}
\label{sec-1}
\subsection{leetcode}
\label{sec-1-1}
\subsection{C/C++}
\label{sec-1-2}
\subsubsection{\textbf{TODO} function template}
\label{sec-1-2-1}
\subsubsection{\textbf{TODO} iostream/fiostream}
\label{sec-1-2-2}
\subsubsection{\textbf{TODO} dynamic memory allocation in C and C++}
\label{sec-1-2-3}
\subsubsection{\textbf{TODO} Error Handling in C and C++}
\label{sec-1-2-4}
\subsubsection{\textbf{TODO} namespace in C and C++}
\label{sec-1-2-5}
\subsubsection{\textbf{TODO} dynamic$_{\mathrm{cast}}$, static$_{\mathrm{cast}}$, interpret$_{\mathrm{cast}}$}
\label{sec-1-2-6}
\subsubsection{\textbf{TODO} smart ptr, unique ptr}
\label{sec-1-2-7}
\subsection{Python}
\label{sec-1-3}
\subsection{Distributed System+Map/Reduce+Hadoop+MPI+Spark}
\label{sec-1-4}
\section{Machine Learning}
\label{sec-2}
\subsection{Neural Network}
\label{sec-2-1}
\subsubsection{\textbf{TODO} Paper reviews on Deep Network}
\label{sec-2-1-1}

    \texttt{DEADLINE:} \textit{2015-07-22 Wed}

\begin{enumerate}
\item \emph{Learning multiple layers of representation (By Hinton, 2007)}
\begin{itemize}
\item \textbf{Explain away} phenomenon in directed network, i.e., v-structure, which may result in the computational challenging when training.
\item Unsupervised, undirected, layer by layer, and fine-tune network learning.
\end{itemize}
\item \emph{Representation Learning: A Review and New Perspectives (By Bengio, 2012)}
\begin{itemize}
\item \textbf{Smooth} means local generalization.
\item Transfer Learning by Deep Learning.
\end{itemize}
\item \emph{UFLDL Tutorial (Online,2015)}
\begin{itemize}
\item \textbf{Convolutional} means local summary.
\item \textbf{Back propagation} Errors from top to bottom. Note the delta on exponential family has specific formula.
\end{itemize}
\end{enumerate}
\subsection{Conditional Random Field}
\label{sec-2-2}
\subsection{Regression}
\label{sec-2-3}
\subsection{Kernal (plus SVM \& Gaussian Process)}
\label{sec-2-4}
\subsection{Monte Carlo}
\label{sec-2-5}
\subsubsection{\textbf{TODO} HMC and SMC}
\label{sec-2-5-1}
\subsection{Regulation Bayesian}
\label{sec-2-6}
\subsection{Common Optimization Methods.}
\label{sec-2-7}
\section{Research}
\label{sec-3}
\subsection{RIP3}
\label{sec-3-1}
\subsubsection{\textbf{TODO} Compounds Collection.}
\label{sec-3-1-1}
\subsubsection{\textbf{TODO} Prediction by DrugCIPHER and GIFT.}
\label{sec-3-1-2}
\subsection{RSI}
\label{sec-3-2}
\subsection{Transfer Learning}
\label{sec-3-3}
\subsubsection{\textbf{TODO} Compounds Feature Selection.}
\label{sec-3-3-1}
\subsubsection{\textbf{TODO} Construct the Algorithm by Pure C++ or Python with C.}
\label{sec-3-3-2}
\subsubsection{\textbf{TODO} Deep Learning on Transfer Multi-task or Feature Representation.}
\label{sec-3-3-3}
\subsection{GIFT}
\label{sec-3-4}
\subsubsection{\textbf{TODO} R Package Establish.}
\label{sec-3-4-1}
\subsubsection{\textbf{TODO} Update the Results by Pulling More Data.}
\label{sec-3-4-2}
\section{Finding Jobs}
\label{sec-4}
\subsection{IBM}
\label{sec-4-1}
\subsection{Microsoft}
\label{sec-4-2}
\subsection{Baidu}
\label{sec-4-3}
\subsection{Ali}
\label{sec-4-4}
\subsection{Hulu}
\label{sec-4-5}
\section{Finding postdoc}
\label{sec-5}
\subsection{Jun Liu}
\label{sec-5-1}
\subsection{Wing Hong Wong}
\label{sec-5-2}
\subsection{Michigan\ldots{}}
\label{sec-5-3}
\section{CV Modification}
\label{sec-6}

\end{document}
